Effectiveness of community-based TURF-reserves in small-scale fisheries

### 2018-12-04 docs/paper/Villasenor-Derbez.Rmd
Added a paragraph explaining why we do each analysis to close #24 and similar to #32

TURF-reserve systems are inherently intrincate social-ecological systems, and their effectiveness must depend on how environmental and social factors combine and interact \citep{gelcich_2015}. This is especially important in social-ecological coastal systems dominated by close interactions and feedbacks between people and natural resources \citep{ostrom_2009-hg}. There is a growing body of literature focusing on the relations between socioeconomic and governance structures and reserve effectiveness \citep{halpern_2013,lpezangarita_2014,mascia_2017-m_,bergseth_2018}. However, to our knowledge, no studies exist that evaluate TURF-reserves from both a social and ecological perspective.

@@

@@

## Study area

@@

>>>>

TURF-reserve systems are inherently intrincate social-ecological systems, and their effectiveness must depend on how environmental and social factors combine and interact \citep{gelcich_2015}. This is especially important in social-ecological coastal systems dominated by close interactions and feedbacks between people and natural resources \citep{ostrom_2009}. There is a growing body of literature focusing on the relations between socioeconomic and governance structures and reserve effectiveness \citep{halpern_2013,lpezangarita_2014,mascia_2017-m_,bergseth_2018}. However, to our knowledge, no studies exist that evaluate TURF-reserves from both a social and ecological perspective.

@@

## TURF-reserves in Mexico

@@

## Study areas

@@

The regulation governing the implementation of Fish refuges states that these are fishery management tools intended to have biological or socioeconomic benefits \citep{nom}. For this reason, the main portion of our analyses focuses on a series of biological and socioeconomic indicators that may respond to reserve implementation. However, the effectiveness of conservation and fisheries management interventions also depends on the social and governance structures in place. We therefore incorporate a reduced version of the Social Ecological Systems framework \citep{ostrom_2009} and evaluate variables and indicators known to aid and hinder the effectiveness of management interventions in conservation and fisheries. The incorporation of the SES is not intended to relate different levels of governance with reserve effectiveness, but rather provide a discussion of potential causes of individual reserve performance. The following two sections describe our data collection methods and analyses of biological and socioeconomic indicators as well as the SES analysis.
